Analysis

### 2022-05-25 code/R/Analysis.Rmd
File cleanup

# Camera codes:
# 2018 NARS-04: 2018 NARS A
# 2018 THUL-01: 2018 THUL B
# 2019 NARS-13: 2019 NARS C
# 2019 NARS-17: 2019 NARS D
# 2019 NYAA-04: 2019 NYAA E

@@

@@

```{r fig.height=4}
d2 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_THUL-01_Evaluate.csv")

@@

```{r}
# NYAA-04 gt:
thul01_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_15_NorwayAnnotations_THUL-01_IndividualAnnotations_FRCNN_Metrics.csv")

@@

```
```{r}
# Minimum mm: 0-160, 0 + 200-1000, 10, 0, 1, 6
# All zero: 0, 0, 0, 8, 0.9885551, 6
# Correct noo with minimum mm: 0-160, 0 + 200-1000, 10, 0, 1, 6

@@

NARS13_p1 = d4 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NARS-13 Parameter combination") +
  facet_wrap(vars(as.factor(maxDist))) +
  scale_color_gradient(low="blue", high="red")

NARS13_p2 = d4 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm)) + 
  ggtitle("NARS-13 Ten lowest mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_AllCombinations.png', NARS13_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_TenLowest.png', NARS13_p2)

>>>>

# Camera codes:
# 2018 NARS-04: 2018 NARS A
# 2018 THUL-01: 2018 THUL B v
# 2019 NARS-13: 2019 NARS C
# 2019 NARS-17: 2019 NARS D v
# 2019 NYAA-04: 2019 NYAA E

@@

####### MMFIX PARAMETER TEST ########

# NYAA-04
```{r fig.height=4}
NYAA04d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/NYAA-04_parameterTest_Evaluation.csv")

NYAA04_p1 = NYAA04d1 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Parameter combination") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

NYAA04_p2 = NYAA04d1 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Ten Lowest Mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NYAA-04_AllCombinations.png', NYAA04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NYAA-04_TenLowest.png', NYAA04_p2)

rm(NYAA04_p1)
rm(NYAA04_p2)
```

# NARS-13
```{r fig.height=4}
NARS13d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/NARS-13_parameterTest_Evaluation.csv")

NARS13_p1 = NARS13d1 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Parameter combination") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

NARS13_p2 = NARS13d1 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Ten Lowest Mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-13_AllCombinations.png', NARS13_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-13_TenLowest.png', NARS13_p2)

rm(NARS13_p1)
rm(NARS13_p2)
```

# NARS-04
```{r fig.height=4}
NARS04d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/NARS-04_parameterTest_Evaluation.csv")

NARS04_p1 = NARS04d1 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Parameter combination") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

NARS04_p2 = NARS04d1 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Ten Lowest Mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-04_AllCombinations.png', NARS04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-04_TenLowest.png', NARS04_p2)

rm(NARS04_p1)
rm(NARS04_p2)
```

# NARS-17
```{r fig.height=4}
NARS17d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/NARS-17_parameterTest_Evaluation.csv")

NARS17_p1 = NARS17d1 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Parameter combination") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

NARS17_p2 = NARS17d1 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Ten Lowest Mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-17_AllCombinations.png', NARS17_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/NARS-17_TenLowest.png', NARS17_p2)

rm(NARS17_p1)
rm(NARS17_p2)
```

# THUL-01
```{r fig.height=4}
THUL01d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/THUL-01_parameterTest_Evaluation.csv")

THUL01_p1 = THUL01d1 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Parameter combination") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

THUL01_p2 = THUL01d1 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NYAA-04 Ten Lowest Mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/THUL-01_AllCombinations.png', THUL01_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/figures/THUL-01_TenLowest.png', THUL01_p2)

rm(THUL01_p1)
rm(THUL01_p2)
```

### Explore combinations

# NYAA-04
```{r echo = FALSE}
print("NYAA-04")
nyaa04_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2021_12_13_NorwayAnnotations_NYAA-04_IndividualAnnotations_FRCNN_Metrics.csv")

print('True number of flowers')
length(unique(nyaa04_gt$id_gt))

# Minimum mm
print("Lowest number of mismatches")
min(NYAA04d1$mm)
NYAA04Minmm = NYAA04d1[NYAA04d1$mm == min(NYAA04d1$mm),]

# All zero
NYAA04AllZero = NYAA04d1 %>% 
  filter(maxDisap == 0 & maxDist == 0 & runMean == 0)

# Correct number of flowers and minimum mm
NYAA04CorrectflowerMinmm = NYAA04d1 %>% 
  filter(number_of_objects == length(unique(nyaa04_gt$id_gt)))
NYAA04CorrectflowerMinmm = NYAA04CorrectflowerMinmm[NYAA04CorrectflowerMinmm$mm == min(NYAA04CorrectflowerMinmm$mm),]
```

# NARS-13
```{r echo = FALSE}
print("NARS-13")
nars13_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_04_30_NorwayAnnotations_NARS-13_IndividualAnnotations_FRCNN_Metrics.csv")

print('True number of flowers')
length(unique(nars13_gt$id_gt))

# Minimum mm
print("Lowest number of mismatches")
min(NARS13d1$mm)
NARS13Minmm = NARS13d1[NARS13d1$mm == min(NARS13d1$mm),]

# All zero
NARS13AllZero = NARS13d1 %>% 
  filter(maxDisap == 0 & maxDist == 0 & runMean == 0)

# Correct number of flowers and minimum mm
NARS13CorrectflowerMinmm = NARS13d1 %>% 
  filter(number_of_objects == length(unique(nars13_gt$id_gt)))
NARS13CorrectflowerMinmm = NARS13CorrectflowerMinmm[NARS13CorrectflowerMinmm$mm == min(NARS13CorrectflowerMinmm$mm),]
```

# NARS-04
```{r echo = FALSE}
print("NARS-04")
nars04_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_17_NorwayAnnotations_NARS-04_IndividualAnnotations_FRCNN_Metrics.csv")

print('True number of flowers')
length(unique(nars04_gt$id_gt))

# Minimum mm
print("Lowest number of mismatches")
min(NARS04d1$mm)
NARS04Minmm = NARS04d1[NARS04d1$mm == min(NARS04d1$mm),]

# All zero
NARS04AllZero = NARS04d1 %>% 
  filter(maxDisap == 0 & maxDist == 0 & runMean == 0)

# Correct number of flowers and minimum mm
NARS04CorrectflowerMinmm = NARS04d1 %>% 
  filter(number_of_objects == length(unique(nars04_gt$id_gt)))
NARS04CorrectflowerMinmm = NARS04CorrectflowerMinmm[NARS04CorrectflowerMinmm$mm == min(NARS04CorrectflowerMinmm$mm),]
```

# NARS-17
```{r echo = FALSE}
print("NARS-17")
nars17_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2021_12_30_NorwayAnnotations_NARS-17_IndividualAnnotations_FRCNN_Metrics.csv")

print('True number of flowers')
length(unique(nars17_gt$id_gt))

# Minimum mm
print("Lowest number of mismatches")
min(NARS17d1$mm)
NARS17Minmm = NARS17d1[NARS17d1$mm == min(NARS17d1$mm),]

# All zero
NARS17AllZero = NARS17d1 %>% 
  filter(maxDisap == 0 & maxDist == 0 & runMean == 0)

# Correct number of flowers and minimum mm
NARS17CorrectflowerMinmm = NARS17d1 %>% 
  filter(number_of_objects == length(unique(nars17_gt$id_gt)))
NARS17CorrectflowerMinmm = NARS17CorrectflowerMinmm[NARS17CorrectflowerMinmm$mm == min(NARS17CorrectflowerMinmm$mm),]
```

# THUL-01
```{r echo = FALSE}
print("THUL-01")
thul01_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_15_NorwayAnnotations_THUL-01_IndividualAnnotations_FRCNN_Metrics.csv")

print('True number of flowers')
length(unique(thul01_gt$id_gt))

# Minimum mm
print("Lowest number of mismatches")
min(THUL01d1$mm)
THUL01Minmm = THUL01d1[THUL01d1$mm == min(THUL01d1$mm),]

# All zero
THUL01AllZero = THUL01d1 %>% 
  filter(maxDisap == 0 & maxDist == 0 & runMean == 0)

# Correct number of flowers and minimum mm
THUL01CorrectflowerMinmm = THUL01d1 %>% 
  filter(number_of_objects == length(unique(thul01_gt$id_gt)))
THUL01CorrectflowerMinmm = THUL01CorrectflowerMinmm[THUL01CorrectflowerMinmm$mm == min(THUL01CorrectflowerMinmm$mm),]
```

####### /MMFIX PARAMETER TEST ########

@@

# After MMFix
```{r fig.height=4}
d2 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/MMFix/THUL-01_parameterTest_Evaluation.csv")

@@

```{r fig.height=4}
# d2 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_THUL-01_Evaluate.csv")
# 
# 
# THUL01_p1 = d2 %>% 
#   ggplot() +
#   geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
#   ggtitle("THUL-01 Parameter combination") +
#   facet_wrap(vars(as.factor(maxDist)))
# 
# 
# THUL01_p2 = d2 %>% 
#   arrange(mm, ascending = T) %>% 
#   filter(mm == 0) %>% 
#   ggplot() +
#   geom_point(aes(x=runMean, y = maxDisap, size = mm)) + 
#   ggtitle("THUL-01 All zero mismatches") +
#   facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")
# 
# 
# THUL01_p1
# THUL01_p2
# 
# ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllCombinations.png', THUL01_p1)
# ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllZero.png', THUL01_p2)
```

```{r}
# THUL-01 gt:
thul01_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_15_NorwayAnnotations_THUL-01_IndividualAnnotations_FRCNN_Metrics.csv")

@@

```{r}
# Minimum mm: 0-160, 0 + 200-1000, 10, 0, 1, 6
# All zero: 0, 0, 0, 8, 0.9885551, 6
# Correct noo with minimum mm: 0-160, 0 + 200-1000, 10, 0, 1, 6

@@

NARS04_p1 = d4 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NARS-13 Parameter combination") +
  facet_wrap(vars(as.factor(maxDist))) +
  scale_color_gradient(low="blue", high="red")

NARS04_p2 = d4 %>% 
  arrange(mm, ascending = T) %>% 
  slice_head(n = 10) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm)) + 
  ggtitle("NARS-13 Ten lowest mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_AllCombinations.png', NARS04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-13_TenLowest.png', NARS04_p2)
